---
name: Erik Fasterius
position: Bioinformatician
# email: erik.fasterius@outlook.com
# date: "`r format(Sys.time(), '%B, %Y')`"
# profilepic: ../assets/img/profile-picture.jpg
headcolor: 0055A0
www: fasterius.github.io
github: fasterius
linkedin: erik-fasterius
fontsize: 10pt
output: vitae::moderncv
---

```{r Setup, include = FALSE}
# Chunk options
knitr::opts_chunk$set(echo    = FALSE,
                      warning = FALSE,
                      message = FALSE)

# Load packages
suppressPackageStartupMessages(library("vitae"))

# Read and filter data
data <- read.table("data/cv-data.tsv",
                   sep              = "\t",
                   header           = TRUE,
                   stringsAsFactors = FALSE)
data <- data %>% filter(show == "TRUE")
```

# About me

I am a bioinformatician and scientist working mainly with computational
biology, pipeline development and advanced training. I come from a background
in biotechnology and thus have a deep understanding of both bioinformatics and
the underlying biology. I have experience working with machine learning,
software development, cancer biology, drug screening and cell line
authentication. Additional special interests include reproducibility and data
visualization. \

I am analytically minded, thorough and enjoy problem-solving at all levels. I
have always liked sharing my knowledge with others, be that through more
traditional teaching avenues or through corridor-conversations with colleagues.
Learning new things is something I have always appreciated. I'm creative,
adaptable and social. \

At my current workplace, the National Bioinformatics Infrastructure Sweden
(NBIS), I offer advanced bioinformatic support and guidance to life science
researchers in Sweden through the SciLifeLab community. My current focus
involves transcriptomics and its applications in bulk and single cell RNA
sequencing, as well as several pipeline development projects. I am also engaged
in advanced computational biology and data analysis training at the European
level through ELIXIR. My work at NBIS allows me to help life science
researchers in Sweden bring their projects to completion with tailor-made
bioinformatics solutions, which is something I greatly enjoy. \

# Employment

```{r Employment}
data %>%
    filter(type == "employment") %>%
    detailed_entries(
        when  = glue::glue("{`date_start`} - {`date_end`}"),
        what  = `what`,
        with  = `with`,
        where = `where`)
```

# Education

```{r Education}
data %>%
    filter(type == "education") %>%
    detailed_entries(
        when  = glue::glue("{`date_start`} - {`date_end`}"),
        what  = `what`,
        with  = `with`,
        where = `where`)
```

## Selected courses

```{r Selected courses}
data %>%
    filter(type == "course") %>%
    detailed_entries(
        when  = glue::glue("{`date_end`}"),
        what  = `what`,
        with  = `with`,
        where = `where`)
```


# Teaching

I have been involved in a number of advanced courses related to bioinformatics
in the last few years. All of the courses are offered to PhD students,
post-docs and other high-level researchers in Sweden (NBIS), Switzerland (SIB)
and other countries in the ELIXIR network. I am a Course Leader for the Tools
for Reproducible Research NBIS course. I am also a certified Carpentry
Instructor. I have taught in both classroom and online settings. \

```{r Teaching}
data %>%
    filter(type == "teaching") %>%
    detailed_entries(
        when  = glue::glue("{`date_end`}"),
        what  = `what`,
        with  = `with`,
        where = `where`)
```

# Resources

```{r Resources}
data %>%
    filter(type == "resource") %>%
    detailed_entries(
        what  = `what`,
        with  = `with`)
```

# Publications

```{r publications}
bibliography_entries("data/publications.bib")
```
